---
title: "Bayesian_test_environment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Libraries that are going to be used

```{r}

library(rjags)
library(rstan)

```

## Checking that Rstan is properly installed

Prior to the tutorial make sure that the script below runs without error on your R installation.
What you need is a working installation of Stan: http://mc-stan.org/ .
For installation instructions, see here: 
https://github.com/stan-dev/rstan/wiki/RStan-Getting-Started

After installation you should be able to run this script which should output
some summary statistics and some pretty plots, :)

Generating some fake data:
 
```{r}
set.seed(123)
y <- rbinom(30, size = 1, prob = 0.2016)

```
 
Fitting binomial data
 
```{r}
model_string <- "
data {
  int n;
  int y[n];
}
parameters {
  real<lower=0, upper=1> theta;
}
model {
  y ~ bernoulli(theta);
}"

stan_samples <- stan(model_code = model_string, data = list(y = y, n = length(y)) )
stan_samples
traceplot(stan_samples)
plot(stan_samples)
```
 
 
 
 
 
 
 