---
title: "MB_exercise2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



We might need it
#y[i]~dbern(p[i])
#logit(p[i])<-inprod(brta[],x[,i])
#y[i]~dbern(p[i])
#p[i]<-invlogit(inprod(brta[],x[,i]))














Load libraries
```{r}
library(tidyverse)
library(R2jags)
library(coda)
```


```{r}
heart <- read_csv("heart.csv") # %>%

for (i in c(2,3,6,7, 9, 11, 12, 13, 14)) {
  heart[[i]] <- as_factor(heart[[i]] - 1)
}
heart
```



```{r}
X <- model.matrix(target ~ ., data = heart)
n <- nrow(X)
k <- ncol(X)
```


```{r}
model_code <- "
model
{
  # Likelihood
  for (i in 1:n) {
    y[i] ~ dbern(min(max(eta[i])))
    logit(eta[i]) <- inprod(beta[], X[i,])
  }

  # Priors
  for (j in 1:k) {
    beta[j] ~ dnorm(0, 0.005^-2)
  }
}
"

```

```{r}
model_data <- list(n = n, k = k, y = heart$target, X = X)
model_parameters <- c("beta")
```




```{r}
model_run <- jags(
  data = model_data,
  parameters.to.save = model_parameters,
  model.file = textConnection(model_code),
  n.chains = 4,
  n.iter = 1000,
  n.burnin = 200,
  n.thin = 2
)
```


























