---
title: "Project1_59606"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Loading all libraries.

```{r}
library(tidyverse)
library(R2jags)
library(coda)
```


With infection as the target variable, choose and adjust an adequate
Bayesian regression model (linear, generalized linear or logistic) on a training
subset of the whole data, using a Monte Carlo Markov Chain procedure.

Load dataset and examine it.

```{r}
infection <- read_csv("infections.csv"); infection
```


```{r}
infection$infection<-ifelse(as.character(infection$infection) == "Yes", 1, 0)
infection$sex<-ifelse(as.character(infection$sex) == "F", 1, 0)
infection$prevAB<-ifelse(as.character(infection$prevAB) == "Yes", 1, 0)
infection
```



```{r}
for (i in c(3, 5, 8)) {
  infection[[i]] <- as_factor(infection[[i]])
}

for (i in c(1, 2, 4, 6, 7)) {
  infection[[i]] <- scale(infection[[i]])
}
infection
```





Check for the convergence of the generated chains.



Determine if the model is suitable by comparing it with a null (with no
covariates) model, using the Bayes factor.



Present a predictive performance measure of the model using the test
subset (remaining observations).




Produce a report with the results of the data analysis, with all the code
used.








